### 2016-06-22 sec4_baseline.tex
Commit first
Updates on Experiments Graphs

It is obvious that we cannot simply split the trajectory database into disjoint partitions because a GCMP pattern requires $L$-consecutive and the corresponding segments may cross multiple partitions. Our strategy is to use data replication to enable parallel mining. Each snapshot will replicate its clusters to $\eta$ preceding snapshots. In other words, the partition for the snapshot $S_t$ contains clusters in $S_t$, $S_{t+1}\ldots,S_{t+\eta}$. Determining a proper $\eta$ is critical in ensuring the
correctness and efficiency of TRPM. If $\eta$ is too small, certain cross-partition patterns may be missed. If $\eta$ is set too large, expensive network communication and CPU processing costs would be incurred in the map and reduce phrases respectively.

To guarantee that no valid pattern is missing, we enforce the
following statement on $\eta$:
I HAVE NO IDEA WHAT YOU ARE TALKING ABOUT STARTING FROM HERE!!!
 \emph{Let $T'$ be the \emph{shortest} 
valid subsequence (wrt. $K,L,G$) of a valid temporal sequence $T$. 
Then, $\eta$ needs to be the upper bound for all $T'$ among all valid temporal sequences to ensure the completeness.} 
Finding the \emph{minimum} $\eta$ is not
straightforward. We notice the minimum $\eta$ is related to the temporal
parameters $K,L,G$ by making the following observation on $G=1$:

@@

\begin{proof}
When $G = 1$, we have demonstrated $\eta=K$
in the above observation. When $G \geq 2$, we compute $\eta$ as follows:
any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
and $n-1$ gaps with sizes $g_1,...,g_{n-1}$.
Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
as follows:
\begin{equation}
\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
\end{equation}
With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$; (2)
$\forall g_i, 1 \leq g_i \leq G-1 $; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. Constraints (1)(2)(3) due to the 
validity of $T'$ and $G\geq 2$ (4) is because $|T'|$ is minimum.
Based on (1)(3)(4), we can derive (5):  $n \in [1, \lceil \frac{K}{L} \rceil]$.
Constraints (1)-(5) form a convex polygon and $\eta$ is monotone
increasing wrt. $n, l_i, g_i$, therefore, the maximum value of $\eta$ is taken at the upper boundaries
where $g_i = G-1$, 
$\Sigma_{i=1}^{i=n-1}l_i = K-1$, $l_i = K-1$
and $n = \lceil \frac{K}{L} \rceil$. This leads to  $\eta = (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K -2$.
\end{proof}

@@

\begin{algorithm}
\caption{Temporal Replication and Parallel Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K-2$
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...{\eta-1}$}
		\State emit a $\langle \max(t-i,0), S_t \rangle$ pair
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, \lambda_t\rangle$
\State where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{$\langle t,\lambda_t \rangle$}
\State lineSweepMining($\lambda_t$)
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

>>>>

It is obvious that we cannot simply split the trajectory database 
into disjoint partitions because a GCMP pattern requires $L$-consecutiveness 
and the corresponding segments may cross multiple partitions. 
Our strategy is to use data replication to enable parallel mining. 
Each snapshot will replicate its clusters to $\eta-1$ preceding snapshots.
In other words, the partition for the snapshot $S_t$ contains clusters 
in $S_t$, $S_{t+1}\ldots,S_{t+\eta-1}$. 
Determining a proper $\eta$ is critical in ensuring the
correctness and efficiency of TRPM. If $\eta$ is too small, 
certain cross-partition patterns may be missed. 
If $\eta$ is set too large, expensive network communication and 
CPU processing costs would be incurred in the map and reduce phrases respectively.

Before moving on to find the value of $\eta$, 
we first use $\rho_{G,L,K}(T)$ to define the \emph{min-spanned valid subsequence} 
of a sequence $T$. In simple words, $\rho_{G,L,K}(T)$ is the 
subsequence of $T$ with the smallest range and is valid wrt. $K,L,G$. 
%Let $\eta_T$ denote
%the range of $\rho_{G,L,K}(T)$.
To guarantee that no valid patterns are missing, $\eta$ needs
to be greater than the range of $\rho_{G,L,K}(T)$ for any
valid sequence $T$. To see this, consider an arbitrary valid sequence $T$.
Since each partition contains $\eta$ snapshots,
if $\eta \geq \range(\rho_{G,L,K}(T))$ holds, $\rho_{G,L,K}(T)$ must be completely located in one partition. Therefore, the patterns associated with $T$ would not be missing.
Formally, $\eta$ can be computed as:
\begin{equation}
\eta = \max\{\range(\rho_{G,L,K}(T)) | T \text{ is valid wrt. } G,L,K\}
\end{equation}

Directly compute such $\eta$ is challenging. However,
we provide the following theorem which states a bounded estimation on $\eta$: 
\begin{theorem}
\label{THM:RP_ETA}
Let $\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$. Then it guarantees 
the completeness of the partition. Further:
let $\eta^*$ be the optimal value for a given $G,L,K$, then the following holds:
$\eta \leq \eta^* + L-1$.
\end{theorem}
\begin{proof}
See Appendix.
\end{proof}
\eat{
In order to formally compute the minimum value of $\eta$,
we enforce the
following statement on $\eta$:
%I HAVE NO IDEA WHAT YOU ARE TALKING ABOUT STARTING FROM HERE!!!
 \emph{Let $T'$ be the \emph{shortest} 
valid subsequence (wrt. $K,L,G$) of a valid temporal sequence $T$. 
Then, $\eta$ needs to be the upper bound for all $T'$ among all valid temporal sequences to ensure the completeness.} 
Finding the \emph{minimum} $\eta$ is not
straightforward. We notice the minimum $\eta$ is related to the temporal
parameters $K,L,G$ by making the following observation on $G=1$:

@@

\begin{proof}
When $G = 1$, we have demonstrated $\eta=K$
in the above observation. When $G \geq 2$, we compute $\eta$ as follows:
any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
and $n-1$ gaps with sizes $g_1,...,g_{n-1}$.
Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
as follows:
\begin{equation}
\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
\end{equation}
With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$; (2)
$\forall g_i, 1 \leq g_i \leq G-1 $; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. Constraints (1)(2)(3) due to the 
validity of $T'$ and $G\geq 2$ (4) is because $|T'|$ is minimum.
Based on (1)(3)(4), we can derive (5):  $n \in [1, \lceil \frac{K}{L} \rceil]$.
Constraints (1)-(5) form a convex polygon and $\eta$ is monotone
increasing wrt. $n, l_i, g_i$, therefore, the maximum value of $\eta$ is taken at the upper boundaries
where $g_i = G-1$, 
$\Sigma_{i=1}^{i=n-1}l_i = K-1$, $l_i = K-1$
and $n = \lceil \frac{K}{L} \rceil$. This leads to  $\eta = (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K -2$.
\end{proof}
}

@@

\begin{algorithm}
\caption{Temporal Replication and Parallel Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+K+L-1$
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...{\eta-1}$}
		\State emit a $\langle \max(t-i,0), S_t \rangle$ pair
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, \lambda_t\rangle$
\State where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{$\langle t,\lambda_t \rangle$}
\State lineSweepMining($\lambda_t$)
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}
